---
title: "p8105_hw1_dz2426"
author: "Duzhi Zhao"
date: "9/13/2019"
output: github_document
---

# Problem 1

## Section 1
The chunk below creates a data frame containing a random sample of size 8 from a standard normal distribution, a logical vector indicating whether the element of the sample is greater than 0, a character vector of length 8, and a factor vector of length 8 with 3 different factor levels, and also produces the mean of each variable.
```{r}
library(tidyverse)

df_1 = tibble(
  random_samp = rnorm(8),
  log_vec = random_samp > 0,
  char_vec = as.character("a","b","c","d","e","f","g","h"),
  fac_vec = factor(c("jazz","rock","blues","jazz","jazz","rock","blues","rock"))
)

#Take the mean of each variable
mean_random_samp = mean(pull(df_1, random_samp))
mean_log_vec = mean(pull(df_1, log_vec))
mean_char_vec = mean(pull(df_1, char_vec))
mean_fac_vec = mean(pull(df_1, fac_vec))

#Convert the logical, character, and factor vector to numeric variable
as.numeric(pull(df_1, log_vec))
as.numeric(pull(df_1, char_vec))
as.numeric(pull(df_1, fac_vec))

```
Comment 1: 
The mean of the random sample is `r round(mean_random_samp, digits = 2)`. 
The mean of the logic vector is `r round(mean_log_vec, digits = 2)`.
The mean of the character vector is `r round(mean_char_vec, digits = 2)`.
The mean of the factor vector is `r round(mean_fac_vec, digits = 2)`.

Comment 2:
After executing as.numeric function, the logical vector shows a series of "1" and "0", indicating if the statement is true. The character vector still shows "NA" for each data entry and this explains why it does not show a mean value. The factor vector turns out to be a series of number indicating each data entry's corresponding "level". 
This shows that only the numeric and logical vectors can show their mean values, and explains why the character and factor variables did not show their means.

## Section 2
```{r}

```

