---
title: "p8105_hw1_dz2426"
author: "Duzhi Zhao"
date: "9/13/2019"
output: github_document
---

# Problem 1

## Section 1
The chunk below creates a data frame containing a random sample of size 8 from a standard normal distribution, a logical vector indicating whether the element of the sample is greater than 0, a character vector of length 8, and a factor vector of length 8 with 3 different factor levels, and also produces the mean of each variable.
```{r}
library(tidyverse)

df_1 = tibble(
  random_samp = rnorm(8),
  log_vec = random_samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h"),
  fac_vec = factor(c("apple","orange","melon","apple","orange","orange","melon","apple"))
)

mean_random_samp = mean(pull(df_1, random_samp))
mean_log_vec = mean(pull(df_1, log_vec))
mean_char_vec = mean(pull(df_1, char_vec))
mean_fac_vec = mean(pull(df_1, fac_vec))


```
Comments: 
The mean of the random sample is `r round(mean_random_samp, digits = 2)`. 
The mean of the logic vector is `r round(mean_log_vec, digits = 2)`.
The mean of the character vector is `r round(mean_char_vec, digits = 2)`.
The mean of the factor vector is `r round(mean_fac_vec, digits = 2)`.

## Section 2
Here is a code chunk for converting non-numeric variables to numeric variables.
```{r}

```

