---
title: "p8105_hw1_dz2426"
author: "Duzhi Zhao"
date: "9/13/2019"
output: github_document
---

```{r Library}
library(tidyverse)
library(ggplot2)
```

# Problem 1

## Section 1
The chunk below creates a data frame containing a random sample of size 8 from a standard normal distribution, a logical vector indicating whether the element of the sample is greater than 0, a character vector of length 8, and a factor vector of length 8 with 3 different factor levels, and also produces the mean of each variable.
```{r warning = FALSE}

#Data frame
df_1 = tibble(
  random_samp = rnorm(8),
  log_vec = random_samp > 0,
  char_vec = as.character("a","b","c","d","e","f","g","h"),
  fac_vec = factor(c("jazz","rock","blues","jazz","jazz","rock","blues","rock"))
)

#Take the mean of each variable
mean_random_samp = mean(pull(df_1, random_samp))
mean_log_vec = mean(pull(df_1, log_vec))
mean_char_vec = mean(pull(df_1, char_vec))
mean_fac_vec = mean(pull(df_1, fac_vec))

```
Comment 1: <br />
The mean of the random sample is `r round(mean_random_samp, digits = 2)`. <br />
The mean of the logic vector is `r round(mean_log_vec, digits = 2)`. <br />
The mean of the character vector is `r round(mean_char_vec, digits = 2)`. <br />
The mean of the factor vector is `r round(mean_fac_vec, digits = 2)`. <br />
```{r eval = FALSE}
#Convert the logical, character, and factor vector to numeric variable
as.numeric(pull(df_1, log_vec))
as.numeric(pull(df_1, char_vec))
as.numeric(pull(df_1, fac_vec))
```
Comment 2: <br />
After executing as.numeric function, the logical vector shows a series of "1" and "0", indicating if the statement is true. The character vector still shows "NA" for each data entry and this explains why it does not show a mean value. The factor vector turns out to be a series of number indicating each data entry's corresponding "level". 
In general, this shows that the numeric and logical vectors can show their mean values, while the character and factor variables can not.

## Section 2
Here is the second code chunk:
```{r warning = FALSE}

as.numeric(pull(df_1, log_vec)) * pull(df_1, random_samp)
as.factor(pull(df_1, log_vec)) * pull(df_1, random_samp)
as.numeric(as.factor(pull(df_1, log_vec))) * pull(df_1, random_samp)
```
# Problem 2
## Section 1
Here is the data frame for problem 2:
```{r}
#Data frame
df_2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  log_vec_2 = x + y > 1,
  num_vec_2 = as.numeric(log_vec_2),
  fac_vec_2 = as.factor(log_vec_2)
)

#mean, median and standard deviation of x
mean_x = mean(pull(df_2, x))
median_x = median(pull(df_2, x))
sd_x = sd(pull(df_2, x))

#Proportion of cases for which x+y>1
prop_case = mean(pull(df_2, log_vec_2))

```
Description of data frame: <br />
The size of the data set is `r nrow(df_2)` and `r ncol(df_2)`. <br />
The mean, median and standard deviation of x are `r round(mean_x, digits = 2)`, `r round(median_x, digits = 2)` and `r round(sd_x, digits = 2)`, respectively. <br />
The proportion of cases for which x+y>1 is `r round(prop_case, digits = 2)`.

## Section 2
Below are three code chunks for the three yx scatterplots including logical, numerical and factor variables, respectively.
```{r yx_Logical_scatterplot}
ggplot(df_2, aes(x = x, y = y, color = log_vec_2)) +
  geom_point() +
  xlab("x") +
  ylab("y") +
  labs(title = "Logical Variable Scatterplot") +
  theme(legend.position = "right", legend.title = element_blank(),
        plot.title = element_text(color = "black", 
                                  size = 12, 
                                  face = "bold", 
                                  hjust = 0.5))

ggsave("plot_one.png", width = 3, height = 3, scale = 0.75)
```
```{r yx_numeric_scatterplot }

ggplot(df_2, aes(x = x, y = y, color = num_vec_2)) +
  geom_point() +
  xlab("x") +
  ylab("y") +
  labs(title = "Numeric Variable Scatterplot") +
  theme(legend.position = "right", legend.title = element_blank(), 
        plot.title = element_text(color = "black", 
                                  size = 12, 
                                  face = "bold", 
                                  hjust = 0.5))
```
```{r yx_factor_scatterplot}
ggplot(df_2, aes(x = x, y = y, color = fac_vec_2)) +
  geom_point() +
  xlab("x") +
  ylab("y") +
  labs(title = "Factor Variable Scatterplot") +
  theme(legend.position = "right", legend.title = element_blank(),
        plot.title = element_text(color = "black", 
                                  size = 12, 
                                  face = "bold", 
                                  hjust = 0.5))
```
Comment 3: <br />
In line with the value of the proportion of cases for which x+y>1, these three scatterplots clearly show that there is a much higher chance to obtain x+y<1 (red or darker blue dots). On each plot, it also shows that with higher x and y values (green or lighter blue dots), it is more likely to get a 'TRUE' result (x+y>1).





